---
title: "E4_Pipeline_TransformData"
author: "BrinnaeBent"
date: "November 14, 2019"
output: html_document
---

## Read in HR.csv file and transform
```{r}

df <- read.csv("filepath\\HR.csv", header=FALSE, stringsAsFactors = FALSE)


newrow <- rep(NaN, length.out=ncol(df))
df <- rbind(df, newrow)
  
  HR <- function(data){
    E4starttime <- data[1]
    E4 <- data[-c(1,2)]
    E4 <- E4[1:which(is.na(data))[1]]  
    secondspassedE4 <- which(is.na(data))[1]/data[2]
    E4endtime <- E4starttime + secondspassedE4
    E4Time <- as.numeric(seq(from=E4starttime, to=E4endtime, length.out=which(is.na(data))[1]))
  
    HR <- data.frame(E4Time, E4)
    colnames(HR) <- c("Time", "HR")
  
    HR$Time = as.POSIXct(round(as.numeric(HR$Time)), origin = "1970-01-01")
    write.table(HR, file = "filename.csv", sep = ",", append = TRUE, quote = FALSE, col.names = FALSE, row.names = FALSE)

  }
  
  apply(df, 2, HR)

```


```{r}
df <- read.csv("filepath\\IBI.csv", header=FALSE, stringsAsFactors = FALSE)

for (i in seq(1, (length(df)-1), 2)){  #<- changes based on length
  Time <- as.numeric(df[1,i] + df[,i])
  IBI <- df[,i+1]
  IBIdf <- data.frame(Time, IBI)
  IBIdf <- IBIdf[-1,]
  colnames(IBIdf) <- c("Time", "IBI")

  IBIdf$Time = as.POSIXct(round(as.numeric(IBIdf$Time)), origin = "1970-01-01")
  
  IBIdf = na.omit(IBIdf)
  IBIdf <- IBIdf[!(IBIdf$IBI == ""), ]

  write.table(IBIdf, file = "filename.csv", sep = ",", append = TRUE, quote = FALSE, col.names = FALSE, row.names = FALSE)
}
```


## Read in IBI.csv file and transform
```{r}
df <- read.csv("filepath\IBI.csv", header=FALSE, stringsAsFactors = FALSE)


for (i in seq(1, (length(df)-2), 2)){  #<- changes based on length
  Time <- as.numeric(df[1,i] + df[,i])
  IBI <- df[,i+1]
  IBIdf <- data.frame(Time, IBI)
  IBIdf <- IBIdf[-1,]
  colnames(IBIdf) <- c("Time", "IBI")

  IBIdf$Time = as.POSIXct(round(as.numeric(IBIdf$Time)), origin = "1970-01-01")
  
  IBIdf = na.omit(IBIdf)
  IBIdf <- IBIdf[!(IBIdf$IBI == ""), ]

  write.table(IBIdf, file = "filename.csv", sep = ",", append = TRUE, quote = FALSE, col.names = FALSE, row.names = FALSE)
}


```


## Read in ACC.csv file and transform
## This code removes lines where one of X,Y, and Z are NA (Complete data)
```{r}
df <- read.csv("filepath\\ACC.csv", header=FALSE, stringsAsFactors = FALSE)

    
for (i in seq(1, (length(df)-2), 3)){  #<- changes based on length
  
  startTime <- df[1,i]
  secondspassed <- (nrow(df[i])-2)/32
  endtime <- startTime + secondspassed
  Time <- as.numeric(seq(from=startTime, to=endtime, length.out=(nrow(df[i])-2)))
  C1 <- df[-c(1,2),i]
  C2 <- df[-c(1,2),i+1]
  C3 <- df[-c(1,2),i+2]
  
  ACCdf <- data.frame(Time, C1, C2, C3)
  colnames(ACCdf) <- c("Time", "X", "Y", "Z")

  ACCdf$Time = as.POSIXct(round(as.numeric(ACCdf$Time)), origin = "1970-01-01")
  
  ACCdf = na.omit(ACCdf)

  write.table(ACCdf, file = "filename.csv", sep = ",", append = TRUE, quote = FALSE, col.names = FALSE, row.names = FALSE)
}


```



## Read in ACC.csv file and transform
## This is for ACC with incomplete X,Y,Z (Incomplete data, one or more axis not working)
```{r}
df <- read.csv("filepath\\ACC.csv", header=FALSE, stringsAsFactors = FALSE)

    
for (i in seq(1, (length(df)-2), 3)){  #<- changes based on length
  
  lengthnum = which(is.na(df))[i] - 2
  startTime <- df[1,i]
  secondspassed <- (which(is.na(df))[i]-2)/32
  endtime <- startTime + secondspassed
  Time <- as.numeric(seq(from=startTime, to=endtime, length.out=(which(is.na(df))[i]-2)))
  C1 <- df[-c(1,2),i]
  C1 <- C1[1:lengthnum]
  C2 <- df[-c(1,2),i+1]
  C2 <- C2[1:lengthnum]
  C3 <- df[-c(1,2),i+2]
  C3 <- C3[1:lengthnum]
  
  ACCdf <- data.frame(Time, C1, C2, C3)
  colnames(ACCdf) <- c("Time", "X", "Y", "Z")

  ACCdf$Time = as.POSIXct(round(as.numeric(ACCdf$Time)), origin = "1970-01-01")
  
  library(tidyr)
  ACCdf = ACCdf %>% drop_na(X)

  write.table(ACCdf, file = "filename.csv", sep = ",", append = TRUE, quote = FALSE, col.names = FALSE, row.names = FALSE)
}


```

## Read in EDA.csv file and transform
```{r}

df <- read.csv("filepath\\EDA.csv", header=FALSE, stringsAsFactors = FALSE)


newrow <- rep(NaN, length.out=ncol(df))
df <- rbind(df, newrow)

  #data <- df$V9  
EDA <- function(data){
  E4starttime <- data[1]
  E4 <- data[-c(1,2)]
  E4 <- E4[1:which(is.na(data))[1]]  
  secondspassedE4 <- which(is.na(data))[1]/data[2]
  E4endtime <- E4starttime + secondspassedE4
  E4Time <- as.numeric(seq(from=E4starttime, to=E4endtime, length.out=which(is.na(data))[1]))
  
  EDA <- data.frame(E4Time, E4)
  colnames(EDA) <- c("Time", "EDA")
  
  EDA$Time = as.POSIXct(round(as.numeric(EDA$Time)), origin = "1970-01-01")
  
  write.table(EDA, file = "filename.csv", sep = ",", append = TRUE, quote = FALSE, col.names = FALSE, row.names = FALSE)
}

apply(df, 2, EDA)

```


## Read in TEMP.csv file and transform
```{r}

df <- read.csv("filepath\\TEMP.csv", header=FALSE, stringsAsFactors = FALSE)

newrow <- rep(NaN, length.out=ncol(df))
df <- rbind(df, newrow)

  #data <- df$V9  
TEMP <- function(data){
  E4starttime <- data[1]
  E4 <- data[-c(1,2)]
  E4 <- E4[1:which(is.na(data))[1]]  
  secondspassedE4 <- which(is.na(data))[1]/data[2]
  E4endtime <- E4starttime + secondspassedE4
  E4Time <- as.numeric(seq(from=E4starttime, to=E4endtime, length.out=which(is.na(data))[1]))
  
  TEMP <- data.frame(E4Time, E4)
  colnames(TEMP) <- c("Time", "TEMP")
  
  TEMP$Time = as.POSIXct(round(as.numeric(TEMP$Time)), origin = "1970-01-01")
  
  write.table(TEMP, file = "filename.csv", sep = ",", append = TRUE, quote = FALSE, col.names = FALSE, row.names = FALSE)
}  
  apply(df, 2, TEMP)
```


## Read in BVP.csv file and transform
```{r}

  df <- read.csv("filepath\\BVP.csv", header=FALSE, stringsAsFactors = FALSE)

newrow <- rep(NaN, length.out=ncol(df))
df <- rbind(df, newrow)

  data <- df$V9  
BVP <- function(data){
  E4starttime <- data[1]
  E4 <- data[-c(1,2)]
  E4 <- E4[1:which(is.na(data))[1]]  
  secondspassedE4 <- which(is.na(data))[1]/data[2]
  E4endtime <- E4starttime + secondspassedE4
  E4Time <- as.numeric(seq(from=E4starttime, to=E4endtime, length.out=which(is.na(data))[1]))
  
  BVP <- data.frame(E4Time, E4)
  colnames(BVP) <- c("Time", "BVP")
  
  BVP$Time = as.POSIXct(round(as.numeric(BVP$Time)), origin = "1970-01-01")
  
  write.table(BVP, file = "filename.csv", sep = ",", append = TRUE, quote = FALSE, col.names = FALSE, row.names = FALSE)
}  
  apply(df, 2, BVP)

```

